### 2015-01-16 publish/plos_template.tex
added table of commercail comp
edited and spellchecked

Additive manufacturing methods have been under development and use for more than 30 years.
3D printing has experienced a sudden surge in popularity due to recent abalibily of consumer avalible desktop printers. 
3D printing as a form of additive manufacutring has existed for decades although t
The recent avalibility of inexpensive desktop printers have made it fesable for consumers to design and print prototypes and even functional parts, and consumer goods.

The open source software and has spawed the areas of open source hardware, including such as circuit boards computers (arduio, raspberrpi) as well as 3D printers themselves(reprap). 
Open source scientific instruments and laborotory equipment as also being activly developed.
A 3D-printable piece of lab equipment is espically attractive because of the simplicity of downloading and printing a functional object for only the price of the material. 
This may allow a researcher, an oppertunity to preform a measuremt, or activity with out typical finacial and time constraints and with the option of futher customizing the printed part.
Some of the more clever uses of the consumer avalible plastic extrusion printers(fused deposition modeling) is when a printed part is desiged to give a new function to a existig device where before there was none.
For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
Although this may make a rather crude crentrifuge it may be and adqquite method that only costs pennies compared to commerically avalible certirfuges.

Micropipette designs can be found on 3D-part shareing websites.
While exisiting designs require only pen springs, a gasket made from a ballon, and tape, none allow adjustment to know volumes.
We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispenced volume accurately without calibarting with a scale.

@@

>>>>

Although additive manufacturing methods have been under development and use for more than 30 years, 3D printing has experienced a sudden surge in popularity due to recent availability of consumer desktop printers. 
Inexpensive desktop printers have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods.

The open source software movement and has spawned the additional areas of open source hardware, such as circuit boards computers (Arduino, Raspberry Pi) as well as 3D printers themselves (RepRap).
Open source scientific instruments and laboratory equipment as also being actively developed.
A 3D-printable piece of lab equipment is and an attractive idea because of the simplicity of downloading and printing a functional object for only the price of the material. 
This may allow a researcher, an opportunity to preform a measurement, or activity with out typical financial and time constraints and with the option of further customizing the printed object.
Some of the more clever printable parts that have emerged  are ones that give a new function to a existing device where before there was none.
For example a drill bit attachment was designed and printed to hold micro centrifuge tubes allowing a drill to be used for centrifuging samples. 
Although this may make a rather crude centrifuge it may be and adequate method that only costs pennies compared to commercially available centrifuges.

Printable micropipette designs can be found on 3D-part sharing websites.
While existing designs mayb require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes.
We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.

@@

\begin{table}[!ht]
\caption{
\bf{Comparision of Accuracy and Precision}}
\begin{tabular}{|c|c|c|c|}
\hline
    Target Volume & 20 $\mu$L & 50 $\mu$L & 200 $\mu$L  \\
    \hline
    Printed Pipette & 196.4 $\pm$ 2.2 & 53.5 $\pm$ 1.8 & 19.5 $\pm$ 0.6 \\
    Commercial Pipette & 204.5 $\pm$ 2.9 & 49.9 $\pm$ 0.1 & 19.9 $\pm$ 0.2 \\
    \hline
\end{tabular}
\begin{flushleft} Average measured volume by weight and standard deviation.
\end{flushleft}
\label{tab:comp}
 \end{table}
